S-Tipping vs B-Tipping

### 2018-04-21 paper/paper.Rmd
work in progress

$$\tilde F := D_f (F - F_R) $$
$$\frac{d A}{dt} = - q E A_t + sJ $$
$$d \tilde F = \left(-\tilde F - c_{fA} \tilde F A \right) dt  + \sigma_F dW_f$$
$$\alpha := \frac{h+v}{c_{JF}} $$

$$\frac{d J}{dt} = fA -\left(c_{JA} A + \frac{v F}{\alpha + F} \right) J $$

$$\tilde H = D_H (H - H_R) $$
$$d \tilde H = \tilde H \left(1 + \alpha c_{\tilde HP} P - c_{\tilde HF} F\right) dt + \sigma_H dW_h$$

>>>>

$$\tilde F := D_f (F - F_R) $$
$$\frac{d A}{dt} = - q E A_t + sJ $$
$$d \tilde F = - \left(1 + c_{fA} A \right) \tilde F  dt  + \sigma_F dW_f$$
$$\beta := \frac{h+v}{c_{JF}} $$

$$\frac{d J}{dt} = fA -\left(c_{JA} A + \frac{v F}{\beta + F} \right) J $$

$$\tilde H := D_H (H - H_R) $$
$$d \tilde H = \tilde H \left(1 + \alpha c_{\tilde HP} P - c_{\tilde HF} F\right) dt + \sigma_H dW_h$$
